---
output: github_document
bibliography: references.bib
---

<!-- README.md is generated from README.Rmd. Please edit Readme.Rmd. -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


<!-- Define some macros for later use -->
[link-iea]:              https://www.iea.org
[link-ieaeweb]:          https://www.iea.org/data-and-statistics/data-product/world-energy-balances


<!-- badges: start -->
[![R-CMD-check](https://github.com/EnergyEconomyDecoupling/CLPFUDatabase/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/EnergyEconomyDecoupling/CLPFUDatabase/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/CLPFUDatabase)](https://CRAN.R-project.org/package=CLPFUDatabase)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->


# CLPFUDatabase

## Statement of need

Historically, societal exergy analysis (SEA) practitioners have
analyzed the energy conversion chains (ECCs)
of individual countries using linked spreadsheets,
often starting with primary- and final-stage data 
from the [International Energy Agency][link-iea]'s (IEA's)
[extended world energy balances][link-ieaeweb] (EWEBs)
[@Ayres:2003ec; @Serrenho:2014aa; @Brockway:2014aa; @Brockway:2015aa]. 
Data were stored in varying and inconsistent formats.
An early SEA database [@De-Stercke:2014]
estimated energy efficiencies 
of end-use machines using the economic status of countries,
thereby precluding use in energy-economy studies.

Researchers in the field
wanted to expand SEA to cover all countries, but
the spreadsheet approach to SEA was
deemed not scalable.
A new approach to SEA was needed, 
one that scaled across all countries 
for many years without relying on economic data
to estimate machine efficiencies. 

To address that need,
we created a suite of `R` packages 
to support the creation and use of the CL-PFU database.
But creating the CL-PFU database involves 
several `R` packages and
much input data.
A way to streamline the installation of packages was needed,
such that a single `install.packages()` call would
ensure that all dependencies are available.

This package (`CLPFUDatabase`) addresses the need for a simple 
way to install all dependencies.
`CLPFUDatabase` is 
metapackage^[[tidyverse](https://www.tidyverse.org) is another metapackage
             with which many `R` programmers are familiar.], 
whose dependencies include all packages required to make
the CL-PFU database. 
Installation of `CLPFUDatabase` triggers 
installation of all dependencies for the CL-PFU database.


## Installation

You can install `CLPFUDatabase` and all its dependencies
from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("EnergyEconomyDecoupling/CLPFUDatabase")
```


## Dependencies

The packages in the table below are dependencies of `CLPFUDatabase`.

```{r, echo=FALSE, results='asis'}
description <- yaml::read_yaml("DESCRIPTION")
pkg_table <- description |> 
  magrittr::extract2("Imports") |> 
  strsplit(split = ", ") |> 
  data.frame() |> 
  magrittr::set_names("Package name")

# Create a data frame of remotes
remotes <- description |> 
  magrittr::extract2("Remotes") |> 
  strsplit(split = ", ") |> 
  lapply(FUN = strsplit, split = "::|/") |> 
  unlist(recursive = FALSE) |> 
  lapply(FUN = as.list) |> 
  purrr::transpose() |> 
  magrittr::set_names(c("Host", "Organization", "Package name")) |> 
  lapply(FUN = unlist) |> 
  tibble::as_tibble() |> 
  dplyr::mutate(
    Host = dplyr::case_when(
      Host == "github" ~ "GitHub", 
      TRUE ~ Host
    )
  )

# Join the two data frames
dependency_table <- dplyr::left_join(pkg_table, remotes, by = "Package name") |> 
  dplyr::mutate(
    Host = dplyr::case_when(
      is.na(Host) ~ "CRAN", 
      TRUE ~ Host
    )
  )

# Display the table as markdown
knitr::kable(dependency_table)
```

Packages hosted on CRAN can be updated in the "Packages" tab of RStudio.
Users will need to update occasionally packages hosted elsewhere
by using the commands below.

```{r, echo=FALSE, results="asis"}
# Get the table
commands <- dependency_table |> 
  # Filter to GitHub only
  dplyr::filter(Host != "CRAN") |> 
  # Eliminate Host column
  dplyr::mutate(
    Host= NULL
  ) |> 
  # Change order of columns
  dplyr::select(Organization, `Package name`) |> 
  # Transpose 
  as.list() |> 
  unname() |> 
  purrr::transpose() |> 
  # Convert to code with paste0
  sapply(FUN = paste0, collapse = "/") 

commands_list <- paste0("`devtools::install_github(", commands, ")`")

for (this_command in commands_list) {
  cat("\n", this_command, "\n")

}
```



## References
